\section{Field Experience (selection)}

\begin{longtable}{rl}	
\textsc{Septemebr 2015}  & Panormos Project (4 Weeks)\\
&  \textit{Field Walker, Statistics and Open Data specialist}, Intensive Survey \\
& \small{Direction :  \emph{Dr. Anja Slawisch}  | German Archaeological Institute}\\
& \\


\opt{BoLong}{
\textsc{July--October 2013}  & Bo\u{g}azköy-Expedition (11 Weeks)\\
&  \textit{Supervisor}, excavation at ``Kesikkaya Northwest'' \\
& \small{Direction :  \emph{PD. Dr. Andreas Schachner}  | German Archaeological Institute}\\
& \\

\textsc{July--October 2012}  & Bo\u{g}azköy-Expedition (11 Weeks)\\
& Processing the ceramis from the Lower City\\
& \small{Direction :  \emph{PD. Dr. Andreas Schachner}  | German Archaeological Institute}\\
& \\

\textsc{June--October 2011}  &  Bo\u{g}azköy-Expedition (15 Weeks)\\
& \textit{Supervisor}, excavation at ``Kesikkaya Northwest'' \\
& \small{Direction :  \emph{PD. Dr. Andreas Schachner}  | German Archaeological Institute}\\
& \\

\textsc{June--October 2010}  &  Bo\u{g}azköy-Expedition:   (15 Weeks). \\
& \textit{Supervisor}, excavation at ``Kesikkaya Northwest'' \\
& \small{Direction :  \emph{PD. Dr. Andreas Schachner}  | German Archaeological Institute}\\
& \\

\textsc{June--September 2009}  &  Bo\u{g}azköy-Expedition (14 Weeks) \\
& \textit{Supervisor} with M.A. Ingrid DINKEL, excavation at ``Kesikkaya Northwest'' \\
& \small{Direction :  \emph{PD. Dr. Andreas Schachner}  | German Archaeological Institute}\\
& \\
}

\opt{BoShort}{
 \textsc{July--October 2013}    & Bo\u{g}azköy-Expedition (respectively 11, 12, 15, 15 and 14 weeks)\\
 \textsc{\& July--October 2012} & Supervisor of the  excavation at ``Kesikkaya Northwest''\\
 \textsc{\& June--October 2011} & and  Processing the ceramis from the Lower City\\
  \textsc{\& June--October 2010} & Direction :  \emph{PD. Dr. Andreas Schachner} \\
\textsc{\& June--September 2009}& German Archaeological Institute \\
& \\
}
                             
\textsc{August--Juli 2008}  & Albanien, Lac of Prespa \\
& \textit{Archaeologist}: excavation of a neolithic settlement \\
& \small{Direction :  \emph{ Dr. Cécile Oberweiler }  | École Française d’Athènes}\\
& \small{Direction :  \emph{ Prof. Dr. Petrika Lera  }  | University F. Noli of Korçë}\\
& \\

\textsc{June 2008}  & Toumba of Thessaloniki\\
& \textit{Archaeologist}: excavation of a LBA street \\
& \small{Direction: \emph{Prof. Dr. Stelios Andreou}  | University of Thessaloniki}\\
& \\
\end{longtable}
